\documentclass[../DoAn.tex]{subfiles}
\begin{document}

\begin{center}
    \Large{\textbf{ABSTRACT}}\\
\end{center}
\vspace{1cm}
In today's increasingly competitive job market, a well-crafted resume (CV) plays a critical role in the application process. Most enterprises now employ Applicant Tracking Systems (ATS) to automatically screen CVs before they reach human recruiters. However, many candidates, especially fresh graduates, lack the knowledge to optimize their CVs for these systems. Existing online CV builders primarily offer formatting templates without intelligent content analysis, and most have limited support for the Vietnamese language.

This thesis addresses the above problem by leveraging Large Language Models (LLMs), specifically OpenAI GPT, combined with modern web technologies to build the system. The system allows users to upload CVs in PDF or DOCX format, automatically extracts and analyzes content using a hybrid approach that combines traditional text processing techniques with LLM-based parsing, and then provides guided, section-by-section editing through an interactive editor.

The system is built on Next.js 15 with React 19, using TypeScript, with Supabase as the database and Vercel Blob as the file storage service. The key contributions include: (i) a hybrid CV parsing pipeline that saves API tokens while maintaining high accuracy, (ii) an interactive CV editor with drag-and-drop support and auto-save functionality, (iii) CV export to PDF and DOCX formats, and (iv) a two-stage RAG pipeline that matches CVs against job descriptions, with bilingual Vietnamese--English support.

\end{document}
